% http://journal.r-project.org/archive/2009-2/RJournal_2009-2_Williams.pdf

Rattle

•	The development of RATTLE was supported by the Australian tax authority, with the intention of using it to plan their tax-audits.

%-----------------------------------------------------------------------------------------------%
Rattle GUI is a free and open source software(GNU GPL v2) package providing a graphical user interface (GUI) for Data Mining using the R statistical programming language. The source code available at http://rattle.googlecode.com. Rattle is currently used around the world, in a variety of situations. Currently 15 different government departments in Australia, and around the world use Rattle in their data mining activities and as a statistical package.
Rattle provides considerable data mining functionality by exposing the power of the R Statistical Software through a graphical user interface. Rattle is also used as a teaching facility to learn the R software Language. There is a Log Code tab, which replicates the R code for any activity undertaken in the GUI, which can be copied and pasted. Rattle can be used for statistical analysis, or model generation. Rattle allows for the dataset to be partitioned into training, validation and testing. The dataset can be viewed and edited. There is also an option for scoring an external data file.


Rattle (the R Analytical Tool To Learn Easily) provides a simple and logical interface for data mining. It is a new data mining application based on the open source and free statistical language R using the Gnome graphical interface. The application runs under GNU/Linux and MS/Windows. The aim is to provide an intuitive interface that takes you through the basic steps of data mining, as well as illustrating the R code that is used to achieve this. Whilst the tool itself may be sufficient for all of a user's needs, it also provides a stepping stone to more sophisticated processing and modelling in R itself, for sophisticated and unconstrained data mining.


%-----------------------------------------------------------------------------------------------%
File Inputs = CSV, TXT, Excel, ARFF, ODBC, R Dataset, RData File, Library Packages Datasets, Corpus, and Scripts.
Statistics = Min, Max, Quartiles, Mean, St Dev, Missing, Medium, Sum, Variance, Skewness, Kurtosis, chi square.
Statistical tests = Correlation, Wilcoxon-Smirnov, Wilcoxon Rank Sum, T-Test, F-Test, and Wilcoxon Signed Rank.
Clustering = KMeans, Clara, Hierarchical, and BiCluster.
Modeling = Decision Trees, Random Forests, ADA Boost, Support Vector Machine, Logistic Regression, and Neural Net.
Evaluation = Confusion Matrix, Risk Charts, Cost Curve, Hand, Lift, ROC, Precision, Sensitivity.
Charts = Box Plot, Histogram, Correlations, Dendrograms, Cumulative, Principal Components, Benford, Bar Plot, Dot Plot, and Mosaic.
Transformations = Rescale (Recenter, Scale 0-1, Median/MAD, Natural Log, and Matrix) - Impute ( Zero/Missing, Mean, Medium, Mode & Constant), Recode (Binning, Kmeans, Equal Widths, Indicator, Join Categories) - Cleanup (Delete Ignored, Delete Selected, Delete Missing, Delete Obs with Missing)
%-----------------------------------------------------------------------------------------------%
